### 2024-04-27 thesis/chapters/03-design.tex
Export graphs from experiments and prepare outline of thesis

\noindent In accomplishing the objectives of our research we propose several \textbf{goals}:
\begin{todolist}
    \itemsep0pt
    \item Statistically and visually describe vibration signals from the Machinery fault database (MauFaulDa).
    \item Establish a list of conditions that should be later investigated in the experimental setting.
    \item Prepare dataset to be used in conjunction with machine learning models, namely by identifying labels and balancing classes.
    \item Find the best subsets of features in the temporal and spectral domain with previously analyzed feature extraction and selection methods.
    \item Evaluate the performance of models described in the diagnostics section with a significant focus on the k-nearest neighbor algorithm.
    \item Combine feature selection with an online machine learning model.
    \item Acquire measurements of vibrations from machines in the real environment to form a novel dataset of machinery behavior.
    \item Develop hardware and implement its firmware to obtain such measurements of the quality demanded by vibrodiagnostics standards.
\end{todolist}

@@

\section{Dataset exploration}
In establishing the viability of methods to be deployed on the sensor node, we explore the MaFaulDa dataset. It is the largest known machinery fault collection, so it is possible to create multiple subsets based on required conditions.

@@

\begin{figure}[ht]
    \centering
    \begin{subfigure}[b]{0.44\textwidth}
        \includegraphics[width=\textwidth]{assets/design/Mafaulda-A-time-waveform.png}
        \caption{Temporal domain waveforms}
        \label{fig:design:fault-temporal-waveform}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.55\textwidth}
        \includegraphics[width=\textwidth]{assets/design/Mafaulda-A-spectrum-Y-axis.png}
        \caption{Spectra in radial direction}
        \label{fig:design:fault-spectral-waveform}
    \end{subfigure} 
    \caption{Inner bearing vibrations (A) for each fault category with the highest fault severity at 2500 rpm}
\end{figure}

@@

\begin{figure}[ht]
    \centering
    \begin{subfigure}[b]{\textwidth}
        \includegraphics[width=\textwidth]{assets/design/feature-range-temporal.png}
        \caption{Temporal features}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{\textwidth}
        \includegraphics[width=\textwidth]{assets/design/feature-range-spectral.png}
        \caption{Spectral features}
    \end{subfigure}
    \caption{Feature value ranges in inner bearing position (A)}
    \label{fig:design:feature-range}
\end{figure}

@@

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.8\textwidth]{assets/design/pca-explained-variance.png}
    \caption{Number of principal components to cumulative explained variance percentage in the inner bearing position}
    \label{fig:design:pca-explained-variance} 
\end{figure}

@@

\begin{figure}[h!]
    \centering
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{assets/design/pca-loading-plot-temporal.png}
        \caption{Temporal features}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{assets/design/pca-loading-plot-spectral.png}
        \caption{Spectral features}
    \end{subfigure}
    \caption{PCA loading plots for min-max scaled features from the inner bearing position}
    \label{fig:design:pca-loading-plot} 
\end{figure}

@@

\begin{itemize}
\itemsep0pt
\item \textbf{online}: a boolean selector that influences whether metrics are calculated in batch or incremental fashion,
\item \textbf{placement}: chooses between bearing ``A'' and bearing ``B'',
\item \textbf{predicted variable}: select a column out of ``fault'', ``anomaly90'' against which similarity is judged,
\item \textbf{rotational speed limit}: chosses whether only observations occuring within predermined range $2500 \pm 500$ rpm are filtered.
\end{itemize}

@@

\begin{figure}[h!]
    \centering
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{assets/design/approval-voting-temporal.png}
        \caption{Temporal domain features}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{assets/design/approval-voting-spectral.png}
        \caption{Spectral domain features}
    \end{subfigure}
    \caption{Approval rating of the best triplet of features to target variable ``fault'' scored by rank product of correlation, F statistic, and mutual information.}
    \label{fig:design:approval-rating-features}
\end{figure}

@@

\begin{figure}[ht]
    \centering
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{assets/design/KNN-temporal-confusion-matrix-fault.png}
        \caption{Prediction for 6 fault classes in testing set with temporal domain features}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{assets/design/KNN-spectral-confusion-matrix-fault.png}
        \caption{Prediction for 6 fault classes in testing set with spectral domain features}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{assets/design/KNN-temporal-confusion-matrix-anomaly90.png}
        \caption{Prediction of high severity anomalies in testing set with temporal domain features}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{assets/design/KNN-spectral-confusion-matrix-anomaly90.png}
        \caption{Prediction of high severity anomalies in testing set with spectral domain features}
    \end{subfigure}
    \caption{Confusion matrix of k-NN predictions on bearing position A}
    \label{fig:design:KNN-confusion-matrix}
\end{figure}

@@

\begin{table}[h]
\centering
\renewcommand{\arraystretch}{1.2}
\begin{adjustbox}{width=\textwidth}
\begin{tabular}{|l|l|l|rrr|rrr|}
\hline
\multirow{2}{*}{\textbf{\begin{tabular}[c]{@{}l@{}}Bearing\\ position\end{tabular}}} & \multirow{2}{*}{\textbf{\begin{tabular}[c]{@{}l@{}}Target\\ variable\end{tabular}}} & \multirow{2}{*}{\textbf{Observations}}                                             & \multicolumn{3}{l|}{\textbf{Temporal domain}}                                                                                                                                                                                                                                    & \multicolumn{3}{l|}{\textbf{Spectral domain}}                                                                                                                                                                                                                                    \\ \cline{4-9} 
                                                                                     &                                                                                     &                                                                                   & \multicolumn{1}{l|}{\textbf{\begin{tabular}[c]{@{}l@{}}Training\\ accuracy\end{tabular}}} & \multicolumn{1}{l|}{\textbf{\begin{tabular}[c]{@{}l@{}}Testing\\ accuracy\end{tabular}}} & \multicolumn{1}{l|}{\textbf{\begin{tabular}[c]{@{}l@{}}Training\\ F1 score\end{tabular}}} & \multicolumn{1}{l|}{\textbf{\begin{tabular}[c]{@{}l@{}}Training\\ accuracy\end{tabular}}} & \multicolumn{1}{l|}{\textbf{\begin{tabular}[c]{@{}l@{}}Testing\\ accuracy\end{tabular}}} & \multicolumn{1}{l|}{\textbf{\begin{tabular}[c]{@{}l@{}}Training\\ F1 score\end{tabular}}} \\ \hline
\multirow{2}{*}{A}                                                                   & Fault                                                                               & \begin{tabular}[c]{@{}l@{}}$\sum 2998$\\ 498 per class\end{tabular}  & \multicolumn{1}{r|}{0.9859}                                                               & \multicolumn{1}{r|}{0.9736}                                                              & 0.97                                                                                      & \multicolumn{1}{r|}{0.9917}                                                               & \multicolumn{1}{r|}{0.9836}                                                              & 0.98                                                                                      \\ \cline{2-9} 
                                                                                     & \begin{tabular}[c]{@{}l@{}}Anomaly\\ (0.9)\end{tabular}                               & \begin{tabular}[c]{@{}l@{}}$\sum 2454$\\ 1227 per class\end{tabular} & \multicolumn{1}{r|}{0.9869}                                                               & \multicolumn{1}{r|}{0.9800}                                                              & 0.98                                                                                     & \multicolumn{1}{r|}{0.9921}                                                               & \multicolumn{1}{r|}{0.9874}                                                              & 0.99                                                                                      \\ \hline
\multirow{2}{*}{B}                                                                   & Fault                                                                               & \begin{tabular}[c]{@{}l@{}}$\sum 2998$\\ 498 per class\end{tabular}  & \multicolumn{1}{r|}{0.9316}                                                               & \multicolumn{1}{r|}{0.8969}                                                              & 0.90                                                                                     & \multicolumn{1}{r|}{0.9207}                                                               & \multicolumn{1}{r|}{0.8765}                                                              & 0.87                                                                                      \\ \cline{2-9} 
                                                                                     & \begin{tabular}[c]{@{}l@{}}Anomaly \\ (0.9)\end{tabular}                              & \begin{tabular}[c]{@{}l@{}}$\sum 2394$\\ 1197 pre class\end{tabular} & \multicolumn{1}{r|}{0.9568}                                                               & \multicolumn{1}{r|}{0.9273}                                                              & 0.93                                                                                      & \multicolumn{1}{r|}{0.9428}                                                               & \multicolumn{1}{r|}{0.9156}                                                              & 0.92                                                                                      \\ \hline
\end{tabular}
\end{adjustbox}
\caption{k-NN model performance trained on all extracted features}
\label{tab:design:all-extracted-features}
\end{table}

@@

\begin{figure}[ht]
    \centering
    \begin{subfigure}[b]{0.8\textwidth}
        \includegraphics[width=\textwidth]{assets/design/KNN-3-features-combinations-train.png}
        \caption{Testing set}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.8\textwidth}
        \includegraphics[width=\textwidth]{assets/design/KNN-3-features-combinations-test.png}
        \caption{Training set}
    \end{subfigure}
    \caption{Range of prediction accuracy in all k-NN models with subset of 3 features. Subplots show three different predicted variables.}
    \label{fig:design:feature-combinations-KNN}
\end{figure}

@@

\begin{figure}[ht]
    \centering
    \begin{subfigure}[b]{\textwidth}
        \includegraphics[width=\textwidth]{assets/design/best-features-scatter-fault-A-temporal.png}
        \caption{Temporal domain features}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{\textwidth}
        \includegraphics[width=\textwidth]{assets/design/best-features-scatter-fault-A-spectral.png}
        \caption{Spectral domain features}
    \end{subfigure} 
    \caption{Cross sections of 3-dimensional feature spaces with ground truth labels for best attributes. Features are chosen by rank product method.}
    \label{fig:design:feature-space-scatter}
\end{figure}

@@

\begin{figure}[ht]
    \centering
    \begin{subfigure}[b]{\textwidth}
        \includegraphics[width=\textwidth]{assets/design/KNN-feature-selection-predictions-train.png}
        \caption{Testing set}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{\textwidth}
        \includegraphics[width=\textwidth]{assets/design/KNN-feature-selection-predictions-test.png}
        \caption{Training set}
    \end{subfigure} 
    \caption{Batch k-NN algorithm prediction accuracy with various feature sets.}
    \label{fig:design:KNN-accuracy-batch}
\end{figure}

@@

\subsection{Online models}
Online learning imitates hardened conditions for machinery diagnostics that appear in deployment. Delayed provision or omission of actual labels undoubtedly degrades the reliability of the classification. The question is how quickly the accuracy approaches the optimal one from the nearest neighbors trained in batch and what the effect of routine difficulties in the ongoing labeling process is.

@@

\begin{figure}[ht]
    \centering
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{assets/design/Online-event-ordering-fault-train.png}
        \caption{Event ordering of faults}
        \label{fig:design:online-event-order}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{assets/design/Online-severity-levels.png}
        \caption{Fault severity levels ordering}
        \label{fig:design:online-count-severity-level}
    \end{subfigure}
    \caption{Label sequencing for progressive evaluation}
\end{figure}

@@

\begin{figure}[ht]
    \centering
    \begin{subfigure}[b]{\textwidth}
        \includegraphics[width=\textwidth]{assets/design/pca-scatter-online-fault-temporal.png}
        \caption{Principal components from temporal domain features}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{\textwidth}
        \includegraphics[width=\textwidth]{assets/design/pca-scatter-online-fault-spectral.png}
        \caption{Principal components from spectral domain features}
    \end{subfigure}
    \caption{Classification labels in incremental learning \emph{(from left)}: true labels, predicted labels, mistakes in predictions.}
    \label{fig:design:scatter-plot-online}
\end{figure}

>>>>

\noindent In accomplishing the objectives of our research we propose several \textbf{goals}:
\begin{todolist}
    \itemsep0pt
    \item Statistically and visually describe vibration signals from the Machinery fault database (MauFaulDa).
    \item Establish a list of conditions that should be later investigated in the experimental setting.
    \item Prepare dataset to be used in conjunction with machine learning models, namely by identifying labels and balancing classes.
    \item Find the best subsets of features in the temporal and spectral domain with previously analyzed feature extraction and selection methods.
    \item Evaluate the performance of models described in the diagnostics section with a significant focus on the k-nearest neighbor algorithm.
    \item Acquire measurements of vibrations from machines in the real environment to form a novel dataset of machinery behavior.
    \item Develop hardware and implement its firmware to obtain such measurements of the quality demanded by vibrodiagnostics standards.
\end{todolist}

@@

% -------------------------------------------------------------------------------
\clearpage

% All features --------------------------------------------------------
\begin{figure}[ht]
    \centering
    \begin{subfigure}[b]{0.48\textwidth}
        \includegraphics[width=\textwidth]{assets/results/all-features/TD-confusion-matrix.png}
        \caption{Time-domain features}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.48\textwidth}
        \includegraphics[width=\textwidth]{assets/results/all-features/FD-confusion-matrix.png}
        \caption{Frequency-domain features}
    \end{subfigure}
    \caption{All features confusion matrix}
\end{figure}

\begin{figure}[ht]
    \centering
    \begin{subfigure}[b]{0.48\textwidth}
        \includegraphics[width=\textwidth]{assets/results/all-features/TD.png}
        \caption{Time-domain features}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.48\textwidth}
        \includegraphics[width=\textwidth]{assets/results/all-features/FD.png}
        \caption{Frequency-domain features}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.48\textwidth}
        \includegraphics[width=\textwidth]{assets/results/all-features/TD-severity.png}
        \caption{Time-domain features (severity)}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.48\textwidth}
        \includegraphics[width=\textwidth]{assets/results/all-features/FD-severity.png}
        \caption{Frequency-domain features (severity)}
    \end{subfigure} 
    \caption{All features accuracy based on k-value}
\end{figure}

% Standing fan (EDA) --------------------------------------------------------

\begin{figure}[ht]
    \centering
    \begin{subfigure}[b]{0.3\textwidth}
        \includegraphics[width=\textwidth]{assets/results/standing-fan/fan-audio-speed-1.png}
        \caption{Speed 1}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.3\textwidth}
        \includegraphics[width=\textwidth]{assets/results/standing-fan/fan-audio-speed-2.png}
        \caption{Speed 2}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.3\textwidth}
        \includegraphics[width=\textwidth]{assets/results/standing-fan/fan-audio-speed-3.png}
        \caption{Speed 3}
    \end{subfigure}
    \caption{Frequency spectrum from sound of standing fan}
\end{figure}

% Frequency from vibrations
% Plot
\begin{figure}[ht]
    \centering
    \includegraphics[width=0.5\textwidth]{assets/results/standing-fan/standing-fan-accel.png}
    \caption{Estimation of rotation speed from vibrations}
\end{figure}

% Clusters with true labels --------------------------------------------------------------
\begin{figure}[ht]
    \centering
    \begin{subfigure}[b]{0.48\textwidth}
        \includegraphics[width=\textwidth]{assets/results/labels/PCA-TD.png}
        \caption{Time-domain features}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.48\textwidth}
        \includegraphics[width=\textwidth]{assets/results/labels/PCA-FD.png}
        \caption{Frequency-domain features}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.48\textwidth}
        \includegraphics[width=\textwidth]{assets/results/labels/PCA-TD-severity.png}
        \caption{Time-domain features (severity)}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.48\textwidth}
        \includegraphics[width=\textwidth]{assets/results/labels/PCA-FD-severity.png}
        \caption{Frequency-domain features (severity)}
    \end{subfigure} 
    \caption{PCA of all features to 2 components}
\end{figure}

%TODO fix inverse transform
\begin{figure}[ht]
    \centering
    \begin{subfigure}[b]{0.48\textwidth}
        \includegraphics[width=\textwidth]{assets/results/labels/TD.png}
        \caption{Time-domain features}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.48\textwidth}
        \includegraphics[width=\textwidth]{assets/results/labels/FD.png}
        \caption{Frequency-domain features}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.48\textwidth}
        \includegraphics[width=\textwidth]{assets/results/labels/TD-severity.png}
        \caption{Time-domain features (severity)}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.48\textwidth}
        \includegraphics[width=\textwidth]{assets/results/labels/FD-severity.png}
        \caption{Frequency-domain features (severity)}
    \end{subfigure} 
    \caption{3 Best features and their ranges}
\end{figure}

% Incremental learning ------------------------------------------------------

\begin{figure}[ht]
    \centering
    \begin{subfigure}[b]{0.3\textwidth}
        \includegraphics[width=\textwidth]{assets/results/incremental-learning/order-natural.png}
        \caption{Order by raising severity}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.3\textwidth}
        \includegraphics[width=\textwidth]{assets/results/incremental-learning/order-severity.png}
        \caption{Order after relabeing normal class}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.3\textwidth}
        \includegraphics[width=\textwidth]{assets/results/incremental-learning/severity-levels.png}
        \caption{Order of severities}
    \end{subfigure}
    \caption{Ordering of faults}
\end{figure}

% Gradual
\begin{figure}[h]
    \centering
    \begin{subfigure}[b]{0.48\textwidth}
        \includegraphics[width=\textwidth]{assets/results/incremental-learning/gradual-TD.png}
        \caption{Time-domain features}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.48\textwidth}
        \includegraphics[width=\textwidth]{assets/results/incremental-learning/gradual-FD.png}
        \caption{Frequency-domain features}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.48\textwidth}
        \includegraphics[width=\textwidth]{assets/results/incremental-learning/gradual-TD-severity.png}
        \caption{Time-domain features (severity)}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.48\textwidth}
        \includegraphics[width=\textwidth]{assets/results/incremental-learning/gradual-TD-severity.png}
        \caption{Frequency-domain features (severity)}
    \end{subfigure} 
    \caption{Gradual learning (window = 1, skip = 0)}
\end{figure}

% Tumbling windows
\begin{figure}[h]
    \centering
    \begin{subfigure}[b]{0.48\textwidth}
        \includegraphics[width=\textwidth]{assets/results/incremental-learning/tumbling-TD.png}
        \caption{Time-domain features}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.48\textwidth}
        \includegraphics[width=\textwidth]{assets/results/incremental-learning/tumbling-FD.png}
        \caption{Frequency-domain features}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.48\textwidth}
        \includegraphics[width=\textwidth]{assets/results/incremental-learning/tumbling-TD-severity.png}
        \caption{Time-domain features (severity)}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.48\textwidth}
        \includegraphics[width=\textwidth]{assets/results/incremental-learning/tumbling-FD-severity.png}
        \caption{Frequency-domain features (severity)}
    \end{subfigure} 
    \caption{Tumbling window in incremental learning}
\end{figure}

% % Label skips and parts of dataset
\begin{figure}[h]
    \centering
    \begin{subfigure}[b]{0.48\textwidth}
        \includegraphics[width=\textwidth]{assets/results/incremental-learning/all-features-TD-skip.png}
        \caption{Time-domain features}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.48\textwidth}
        \includegraphics[width=\textwidth]{assets/results/incremental-learning/all-features-FD-skip.png}
        \caption{Frequency-domain features}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.48\textwidth}
        \includegraphics[width=\textwidth]{assets/results/incremental-learning/skip-labels-TD.png}
        \caption{Time-domain features}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.48\textwidth}
        \includegraphics[width=\textwidth]{assets/results/incremental-learning/skip-labels-FD.png}
        \caption{Frequency-domain features}
    \end{subfigure} 
    \caption{Skip labels in incremental learning}
\end{figure}

\begin{figure}[h]
    \centering
    \begin{subfigure}[b]{0.48\textwidth}
        \includegraphics[width=\textwidth]{assets/results/incremental-learning/skip-label-TD.png}
        \caption{Time-domain features}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.48\textwidth}
        \includegraphics[width=\textwidth]{assets/results/incremental-learning/skip-label-FD.png}
        \caption{Frequency-domain features}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.48\textwidth}
        \includegraphics[width=\textwidth]{assets/results/incremental-learning/skip-label-TD-severity.png}
        \caption{Time-domain features (severity)}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.48\textwidth}
        \includegraphics[width=\textwidth]{assets/results/incremental-learning/skip-label-FD-severity.png}
        \caption{Frequency-domain features (severity)}
    \end{subfigure} 
    \caption{Skip labels in incremental learning with different sizes}
\end{figure}

% Histograms of machinery measurements
\begin{figure}[h]
    \centering
    \begin{subfigure}[b]{0.33\textwidth}
        \includegraphics[width=\textwidth]{assets/results/histograms/C1.png}
        \caption{C1}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.33\textwidth}
        \includegraphics[width=\textwidth]{assets/results/histograms/C2.png}
        \caption{C2}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.33\textwidth}
        \includegraphics[width=\textwidth]{assets/results/histograms/M1.png}
        \caption{M1}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.33\textwidth}
        \includegraphics[width=\textwidth]{assets/results/histograms/M2.png}
        \caption{M2}
    \end{subfigure} 
    \hfill
    \begin{subfigure}[b]{0.33\textwidth}
        \includegraphics[width=\textwidth]{assets/results/histograms/M3.png}
        \caption{M3}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.33\textwidth}
        \includegraphics[width=\textwidth]{assets/results/histograms/P1.png}
        \caption{P1}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.33\textwidth}
        \includegraphics[width=\textwidth]{assets/results/histograms/P2.png}
        \caption{P2}
    \end{subfigure} 
    \hfill
    \begin{subfigure}[b]{0.33\textwidth}
        \includegraphics[width=\textwidth]{assets/results/histograms/P3.png}
        \caption{P3}
    \end{subfigure} 
    \caption{Histograms}
\end{figure}

% Correlations to RPM
\begin{figure}[h]
    \centering
    \includegraphics[width=0.5\textwidth]{assets/results/feature-values/corr-to-rpm.png}
    \caption{Correlation of features to RPM over all experiments}
\end{figure}

% Features range (3D)
% Standing Fan
\begin{figure}[h]
    \centering
    \begin{subfigure}[b]{0.48\textwidth}
        \includegraphics[width=\textwidth]{assets/results/feature-values/fan-TD-features.png}
        \caption{Time-domain features}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.48\textwidth}
        \includegraphics[width=\textwidth]{assets/results/feature-values/fan-FD-features.png}
        \caption{Frequency-domain features}
    \end{subfigure}
    \caption{Feature range in standing fan}
\end{figure}

% Pumps and compressors
\begin{figure}[h]
    \centering
    \begin{subfigure}[b]{0.48\textwidth}
        \includegraphics[width=\textwidth]{assets/results/feature-values/pumps-TD-dim-3.png}
        \caption{Time-domain features}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.48\textwidth}
        \includegraphics[width=\textwidth]{assets/results/feature-values/pumps-FD-dim-3.png}
        \caption{Frequency-domain features}
    \end{subfigure}
    \caption{Feature range in pumps}
\end{figure}

% Mafaulda
\begin{figure}[h]
    \centering
    \begin{subfigure}[b]{0.48\textwidth}
        \includegraphics[width=\textwidth]{assets/results/incremental-learning/features-TD-dim3-A+B.png}
        \caption{Time-domain features}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.48\textwidth}
        \includegraphics[width=\textwidth]{assets/results/incremental-learning/features-FD-dim3-A+B.png}
        \caption{Frequency-domain features}
    \end{subfigure}
    \caption{Feature range in MaFaulDa}
\end{figure}

% Feature combinations accuracy
\begin{figure}[h]
    \centering
    \begin{subfigure}[b]{0.48\textwidth}
        \includegraphics[width=\textwidth]{assets/results/feature-combinations/fsel-accuracy.png}
        \caption{Accuracy}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.48\textwidth}
        \includegraphics[width=\textwidth]{assets/results/feature-combinations/fsel-percentile.png}
        \caption{Percentile}
    \end{subfigure}
    \caption{Feature selection method choices}
\end{figure}

% In fsel percentile - mention median from notebook for each method - table
\begin{table}[h]
\begin{tabular}{|l|r|r|}
\hline
\textbf{Method}    & \multicolumn{1}{l|}{\textbf{Median percentile {[}\%{]}}} & \multicolumn{1}{l|}{\textbf{Median accuracy {[}\%{]}}} \\ \hline
Rank product       & 93.94                                                    & 81.84                                                  \\ \hline
Mutual information & 93.33                                                    & 81.33                                                  \\ \hline
F statistic        & 91.01                                                    & 81.26                                                  \\ \hline
Correlation        & 84.11                                                    & 79.25                                                  \\ \hline
\end{tabular}
\end{table}

\begin{figure}[h]
    \centering
    \begin{subfigure}[b]{0.48\textwidth}
        \includegraphics[width=\textwidth]{assets/results/feature-combinations/TD-3-features-A-dim3.png}
        \caption{Time domain features}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.48\textwidth}
        \includegraphics[width=\textwidth]{assets/results/feature-combinations/TD-5-neighbors-A-dim3.png}
        \caption{Time domain features}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.48\textwidth}
        \includegraphics[width=\textwidth]{assets/results/feature-combinations/FD-3-features-A-dim3.png}
        \caption{Frequency domain features}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.48\textwidth}
        \includegraphics[width=\textwidth]{assets/results/feature-combinations/FD-5-neighbors-A-dim3.png}
        \caption{Frequency domain features}
    \end{subfigure}
    \caption{Model accuracy distribution}
\end{figure}

\begin{figure}[h]
    \centering
    \includegraphics[width=0.5\textwidth]{assets/results/feature-combinations/model-distr-fsel-k5-f3.png}
    \caption{Model distibution with feature selection methods (k = 5, f = 3)}
\end{figure}

% Counts table

% Best feature selection methods table (order by best count)

% Bearing frequencies table

\clearpage

%TODO ---------------------------------------------------------------------------
\section{Dataset exploration}
In establishing the viability of methods to be deployed on the sensor node, we explore the MaFaulDa dataset. It is the largest known machinery fault collection, so it is possible to create multiple subsets based on required conditions.

@@

\begin{figure}[ht]
    \centering
    \begin{subfigure}[b]{0.44\textwidth}
        \includegraphics[width=\textwidth]{assets/design/Mafaulda-A-time-waveform.png}
        \caption{Time domain waveforms}
        \label{fig:design:fault-temporal-waveform}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.55\textwidth}
        \includegraphics[width=\textwidth]{assets/design/Mafaulda-A-spectrum-Y-axis.png}
        \caption{Spectra in radial direction}
        \label{fig:design:fault-spectral-waveform}
    \end{subfigure} 
    \caption{Inner bearing vibrations (A) for each fault category with the highest fault severity at 2500 rpm}
\end{figure}

@@

%\begin{figure}[ht]
%    \centering
%    \begin{subfigure}[b]{\textwidth}
%        \includegraphics[width=\textwidth]{assets/design/feature-range-temporal.png}
%        \caption{Time-domain features}
%    \end{subfigure}
%    \hfill
%    \begin{subfigure}[b]{\textwidth}
%        \includegraphics[width=\textwidth]{assets/design/feature-range-spectral.png}
%        \caption{Frequency-domain features}
%    \end{subfigure}
%    \caption{Feature value ranges in inner bearing position (A)}
%    \label{fig:design:feature-range}
%\end{figure}

@@

%\begin{figure}[h!]
%    \centering
%    \includegraphics[width=0.8\textwidth]{assets/design/pca-explained-variance.png}
%    \caption{Number of principal components to cumulative explained variance percentage in the inner bearing position}
%    \label{fig:design:pca-explained-variance} 
%\end{figure}

@@

%\begin{figure}[h!]
%    \centering
%    \begin{subfigure}[b]{0.49\textwidth}
%        \includegraphics[width=\textwidth]{assets/design/pca-loading-plot-temporal.png}
%        \caption{Temporal features}
%    \end{subfigure}
%    \hfill
%    \begin{subfigure}[b]{0.49\textwidth}
%        \includegraphics[width=\textwidth]{assets/design/pca-loading-plot-spectral.png}
%        \caption{Spectral features}
%    \end{subfigure}
%    \caption{PCA loading plots for min-max scaled features from the inner bearing position}
%    \label{fig:design:pca-loading-plot} 
%\end{figure}

@@

@@

@@

@@

%\begin{table}[h]
%\centering
%\renewcommand{\arraystretch}{1.2}
%\begin{adjustbox}{width=\textwidth}
%
%\end{tabular}
%\end{adjustbox}
%\caption{k-NN model performance trained on all extracted features}
%\label{tab:design:all-extracted-features}
%\end{table}

@@

@@

%\begin{figure}[ht]
%    \centering
%    \begin{subfigure}[b]{\textwidth}
%        \includegraphics[width=\textwidth]{assets/design/best-features-scatter-fault-A-temporal.png}
%        \caption{Temporal domain features}
%    \end{subfigure}
%    \hfill
%    \begin{subfigure}[b]{\textwidth}
%        \includegraphics[width=\textwidth]{assets/design/best-features-scatter-fault-A-spectral.png}
%        \caption{Spectral domain features}
%    \end{subfigure} 
%    \caption{Cross sections of 3-dimensional feature spaces with ground truth labels for best attributes. Features are chosen by rank product method.}
%    \label{fig:design:feature-space-scatter}
%\end{figure}

@@

%\begin{figure}[ht]
%    \centering
%    \begin{subfigure}[b]{\textwidth}
%        \includegraphics[width=\textwidth]{assets/design/KNN-feature-selection-predictions-train.png}
%        \caption{Testing set}
%    \end{subfigure}
%    \hfill
%    \begin{subfigure}[b]{\textwidth}
%        \includegraphics[width=\textwidth]{assets/design/KNN-feature-selection-predictions-test.png}
%        \caption{Training set}
%    \end{subfigure} 
%    \caption{Batch k-NN algorithm prediction accuracy with various feature sets.}
%    \label{fig:design:KNN-accuracy-batch}
%\end{figure}

@@

\clearpage
\subsection{Online models}
Online learning imitates hardened conditions for machinery diagnostics that appear in deployment. Delayed provision or omission of actual labels undoubtedly degrades the reliability of the classification. The question is how quickly the accuracy approaches the optimal one from the nearest neighbors trained in batch and what the effect of routine difficulties in the ongoing labeling process is.

@@

%\begin{figure}[ht]
%    \centering
%    \begin{subfigure}[b]{0.49\textwidth}
%        \includegraphics[width=\textwidth]{assets/design/Online-event-ordering-fault-train.png}
%        \caption{Event ordering of faults}
%        \label{fig:design:online-event-order}
%    \end{subfigure}
%    \hfill
%    \begin{subfigure}[b]{0.49\textwidth}
%        \includegraphics[width=\textwidth]{assets/design/Online-severity-levels.png}
%        \caption{Fault severity levels ordering}
%        \label{fig:design:online-count-severity-level}
%    \end{subfigure}
%    \caption{Label sequencing for progressive evaluation}
%\end{figure}

@@

%\begin{figure}[ht]
%    \centering
%    \begin{subfigure}[b]{\textwidth}
%        \includegraphics[width=\textwidth]{assets/design/pca-scatter-online-fault-temporal.png}
%        \caption{Principal components from temporal domain features}
%    \end{subfigure}
%    \hfill
%    \begin{subfigure}[b]{\textwidth}
%        \includegraphics[width=\textwidth]{assets/design/pca-scatter-online-fault-spectral.png}
%        \caption{Principal components from spectral domain features}
%    \end{subfigure}
%    \caption{Classification labels in incremental learning \emph{(from left)}: true labels, predicted labels, mistakes in predictions.}
%    \label{fig:design:scatter-plot-online}
%\end{figure}
